Output Summary

### 2023-09-08 03-post-process/output-plots-children/07-capacity-vs-habitat.Rmd
Update text in capacity vs habitat Rmd section

Error bars represent the central 80% of the posterior; grey lines are individual posterior draws of the expected relationship.

>>>>

Error bars represent the central 80% of the posterior for population-specific parr capacity; thin lines are individual posterior draws of the expected relationship, thick line is the posterior mean relationship.
